|

### 2021-07-31 prova_knit_finale.Rmd
small changes to LWF

    \item Compute the weighted average and the variance for the parameters, respectively: $\bar \psi = \sum_{n=1}^N W_{t-1}^n\psi^n$, $\Omega = \sum_{n=1}^N W_{t-1}^n(\psi^n-\bar \psi)(\psi^n-\bar \psi)'$.

@@

Meanwhile, to extract the next period states and parameters it is necessary, firstly, to sample the new $N$ parameter values. Let $\bar \psi$ be the weighted average of the parameter values and $\Omega$ be their variance (the weights used to compute this mean and variance are the previous period inferential ones, i.e. $W_{t-1}^n$).\ \

@@

In fact, let $\pi_{t-1}^N(\psi)=\sum_{n=1}^N \hat W_{t-1}^{A_t^{n}}\cdot \N(\psi^{A_t^{n}},\Omega)$\footnote{Big hat-weights $ \hat W_{t-1}^{A_t^{n}}$ are the normalized weights after the resampling stage, equal to $1/N$ if resampling takes place, $W_{t-1}^n$ otherwise.} be the empirical distribution of the parameters. From the law of iterated expectation and total variance, we obtain:\footnote{For completeness, we specify that the first expected value in the law of iterated expectations and total variances is with respect to the distribution of the indexes and the second one with respect to each of the Normal distributions centered at $\psi^{A_t^{n}}$.}

>>>>

    \item Compute the weighted average and the variance for the parameters, respectively: $\bar \psi = \sum_{n=1}^N \hat W_{t-1}^{A_t^n}\psi^{A_t^n}$, $\Omega = \sum_{n=1}^N \hat W_{t-1}^{A_t^n}(\psi^{A_t^n}-\bar \psi)(\psi^{A_t^n}-\bar \psi)'$.\footnote{Big hat-weights $ \hat W_{t-1}^{A_t^{n}}$ are the normalized weights after the resampling stage, equal to $1/N$ if resampling takes place, $W_{t-1}^n$ otherwise.}

@@

Meanwhile, to extract the next period states and parameters it is necessary, firstly, to sample the new $N$ parameter values. Let $\bar \psi$ be the weighted average of the parameter values and $\Omega$ be their variance (using the normalized weights in $t-1$ after the resampling step).\ \

@@

In fact, let $\pi_{t-1}^N(\psi)=\sum_{n=1}^N \hat W_{t-1}^{A_t^{n}}\cdot \N(\psi^{A_t^{n}},\Omega)$ be the empirical distribution of the parameters. From the law of iterated expectation and total variance, we obtain:\footnote{For completeness, we specify that the first expected value in the law of iterated expectations and total variances is with respect to the distribution of the indexes and the second one with respect to each of the Normal distributions centered at $\psi^{A_t^{n}}$.}
